SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/papersincontext.tex
shortcoming of survey

>>>>

The main shortcoming of this paper was that I didn't attempt to
validate the recorded freshness lifetime against the true change
frequency recorded by \cite{dyldo2} and discussed by
\cite{Dividino2015}. It would be interesting to see how common it is
that the given freshness lifetime, both given as standard-compliant
caching and from existing heuristics, is wrong. There are two types of
errors: That the freshness lifetime is too short, i.e., we could have
cached it longer, and that it is too long, i.e., we would serve stale
data.
